Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-04 ms/manuscript.Rmd
Update MS
add optional highlighting

# SES of morph diversity
f <- ggplot(ses_div_ferns_spatial, aes(fill = mpd_morph_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES MMD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, mpd_morph_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, mpd_morph_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

g <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "MMD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_viridis_c() +
  map_theme

h <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

@@

# SES PE
b <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PE") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pe_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pe_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

>>>>

# SES of morph diversity
f <- ggplot(ses_div_ferns_spatial, aes(fill = mpd_morph_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES MMD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, mpd_morph_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, mpd_morph_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(mpd_morph_obs_p > 0.975 | mpd_morph_obs_p < 0.025) +
  map_theme +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank()
  )

# PD
g <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs)) +
  geom_sf(color = "transparent") +
  labs(fill = "MMD") +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  scale_fill_viridis_c() +
  map_theme

# SES of PD
h <- ggplot(ses_div_ferns_spatial, aes(fill = pd_obs_z)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PD") +
  scale_fill_scico(
    palette = "romaO",
    na.value="grey80",
    direction = -1,
    limits = c(
      -get_limit(ses_div_ferns_spatial, pd_obs_z, "abs"),
      get_limit(ses_div_ferns_spatial, pd_obs_z, "abs")
    )) +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  # highlight only significant cells
  # gghighlight(pd_obs_p > 0.975 | pd_obs_p < 0.025) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )

# To add: RPD
# ggplot(ses_div_ferns_spatial, aes(fill = rpd_obs_z)) +
#   geom_sf(color = "transparent") +
#   labs(fill = "SES RPD") +
#   scale_fill_scico(
#     palette = "romaO",
#     na.value="grey80",
#     direction = -1,
#     limits = c(
#       -get_limit(ses_div_ferns_spatial, rpd_obs_z, "abs"),
#       get_limit(ses_div_ferns_spatial, rpd_obs_z, "abs")
#     )) +
#   scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
#   scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
#   # highlight only significant cells
#   # gghighlight(rpd_obs_p > 0.95 | rpd_obs_p < 0.05) +
#   map_theme +
#   theme(
#     axis.text.y = element_blank()
#   )

@@

# SES PE
b <- ggplot(ses_div_ferns_spatial, aes(fill = pe_obs_p)) +
  geom_sf(color = "transparent") +
  labs(fill = "SES PE") +
  scale_fill_viridis_c() +
  scale_y_continuous(labels = scales::label_number(suffix = "\u00b0N", accuracy = 1)) +
  scale_x_continuous(labels = scales::label_number(suffix = "\u00b0E", accuracy = 1)) +
  map_theme +
  theme(
    axis.text.y = element_blank()
  )
